Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{1.5mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-2mm}}

@@

\begin{figure}
    \includegraphics[height=27mm]{./artwork/guard}

@@

\def\vgap{\vspace{2mm}}
\def\extraspacing{\vspace{2mm} \noindent}

@@

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type1:recur-output}.} We will prove the lemma by providing a way to map each $(k-2)$-tuple $\J(R_1',...,R_{k-2}')$ to a unique $k$-tuple in the H-V $k$-SJ result $\J(R_1,...,R_{k-2},H,V)$.

@@

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type2:recur-output}.} We will prove the lemma by mapping each tuple of $\J(R_1,...,R_{k-3},H',V)$ to a unique tuple in $\J_2$.

>>>>

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-3mm}}

@@

\begin{figure}
    \includegraphics[height=25mm]{./artwork/guard}

@@

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}

@@

\noindent {\bf Proof of Lemma~\ref{lmm:hv:type1:recur-output}.} We will prove the lemma by providing a way to map each $(k-2)$-tuple $\J(R_1',...,R_{k-2}')$ to a unique $k$-tuple in the H-V $k$-SJ result $\J(R_1,...,R_{k-2},H,V)$.

@@

\noindent {\bf Proof of Lemma~\ref{lmm:hv:type2:recur-output}.} We will prove the lemma by mapping each tuple of $\J(R_1,...,R_{k-3},H',V)$ to a unique tuple in $\J_2$.
